---
layout: page
title: Spatial data analysis with R
output:
  md_document:
    variant: gfm
    preserve_yaml: true
editor_options: 
  chunk_output_type: console
---
```{r echo=FALSE}
source("R/functions.R")
```
`r r_studio_header()`

### Additional packages

This course uses a few other packages. Run the following lines of code to 
install them.

```{r, eval=FALSE}
install.packages(c("sf", "tmap", "spData", "raster", "tidyverse"))
```

You should ensure that you have an up-to-date R installation (version 3.5 at least) and that your packages are up-to-date. 
See Chapter 2 of the free online book *Efficient R Programming*, particularly sections 2.3 and 2.5, for details on R installation and [set-up](https://csgillespie.github.io/efficientR/set-up.html).
It is also worth learning the basics of the language, using resources such as "R for Data Science" or interactive guides such as [DataCamp](https://www.datacamp.com/courses/free-introduction-to-r) before proceeding.

The course will be based primarily on the early chapters of the book Geocomputation with R. It may be worth looking at that, particularly the chapter on [getting started](http://geocompr.robinlovelace.net/spatial-class.html), before the course. 
